The value of intermediation

### 2022-09-14 src/presentation/presentation.qmd
Add motivation and fix typos

TODO

@@

::: {.notes}
 - You don't need to think about cooperative game theory in the following part
 - Think of it as a convenient gain sharing rule with some (cooperative and non-cooperative) microfoundations
:::

@@

::: {.notes}
 - Not only platforms. Also describes
   - upstream-downstream setups
   - generally any setting with an important large palyers and many identical small ones
:::

@@

::: {.notes}
 - Skippable if don't have time
:::

@@

::: {.notes}
 - Intentionally simple model
 - Most elemnts borrowed from [@anderson2021hybrid]
:::

@@

::: {.notes}
My contributions
 - Shapley-value is a good fit for platform settings
 - The continuous case is vary tractable in this speciific setting
 - Results about the weighted value are mine
 - Insight that hybrid platforms have higher bargaining power, leading to more distortion
:::

>>>>

 - Bargaining between participants is rather overlooked in platform settings
   - Most papers implicitly assume take-it-or-leave-it offers
 - The use of cooperative bargaining concepts is not widespread in IO
   - Although they are well established in certain subfields, such as upstream-downstream markets
 - Most papers only consider finite-player games
   - Modeling the small players as a continuum simplifies analysis

@@

::: {.notes}
 - You don't need to think about cooperative game theory in the following part
 - Think of it as a convenient gain sharing rule with some (cooperative and non-cooperative) micro-foundations
:::

@@

::: {.notes}
 - Not only platforms. Also describes
   - upstream-downstream setups
   - generally any setting with an important large players and many identical small ones
:::

@@

::: {.notes}
 - Can be skipped if don't have time
:::

@@

::: {.notes}
 - Intentionally simple model
 - Most elements borrowed from [@anderson2021hybrid]
:::

@@

::: {.notes}
My contributions
 - Shapley-value is a good fit for platform settings
 - The continuous case is vary tractable in this specific setting
 - Results about the weighted value are mine
 - Insight that hybrid platforms have higher bargaining power, leading to more distortion
:::
